Report on a Safety Checker for Petri nets

### 2014-01-22 paper/workspace/main.tex
Draft
Fixed typos in draft of math.

  Subprocedure \mathcal{C'} constructs dual state constraints C' corresponding to N and P.
  Subprocedure Model returns assignment A such that A satisfies C'.
  Subprocedure Inv constructs invariant I corresponding to N, P, and A.
\end{verbatim}

@@

\newpage
\section{Method Invariant Minimization}

The method Invariant Minimization constructs an invariant \verb=I= that uses a minimal number places for given Petri net \verb=N= and \verb=P= when \verb=N= never violates \verb=P=.
We present the method Invariant Minimization by example on a simplified mutual exclusion algorithm by Delzanno2001.

@@

@@

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{7cm} | r | r | r | r | } %
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 23 &  0 & 54 &  0 \\
    Invariant \& Invariant Minimization    & 23 &  0 & 54 &  0 \\
    Safety by Refinement                   & 23 &  0 & 54 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \bfc}
\label{bfc-experiments}
\end{table}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{6cm} | r | r | r | r | }
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 14 &  0 & 13 &  0 \\
    Invariant \& Invariant Minimization    & 14 &  0 & 13 &  0 \\
    Safety by Refinement                   & 20 &  0 &  7 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \mist}
\label{mist-experiments}
\end{table}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{6cm} | r | r | r | r | }
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 2 & 0 & 36 & 0 \\
    Invariant \& Invariant Minimization    & 2 & 0 & 26 & 0 \\
    Safety by Refinement                   & 2 & 0 & 36 & 0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \iic}
\label{iic-experiments}
\end{table}

We constructed the following two invariants by applying the method Invariant Minimization.

\begin{itemize}
\item \verb?firewall__no_pred_called_with_zero__depth_2__fixed?: \verb?(assert (<= l3849 0))?
\item \verb?firewall__no_pred_called_with_zero__depth_1__fixed?: \verb?(assert (<= l739 0))?
\end{itemize}

>>>>

  Subprocedure \mathcal{C'} constructs dual state constraints C' corresponding to N and P.
  Subprocedure Model returns assignment A such that A satisfies C'.
  Subprocedure Inv constructs invariant I corresponding to N and A.
\end{verbatim}

@@

\newpage
\section{Method Invariant with Minimization}

The method Invariant with Minimization constructs an invariant \verb=I=
that uses a minimal number of places for given Petri net \verb=N= and
\verb=P= when \verb=N= never violates \verb=P=. 
We present the method Invariant with Minimization by example on a
simplified mutual exclusion algorithm by Delzanno2001.

@@

\begin{verbatim}
* Method Invariant with Minimization

@@

\newpage
\begin{verbatim}
* Method Safety by Refinement:

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{7cm} | r | r | r | r | } %
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals)      & 23 &  0 & 54 &  0 \\
    Invariant \& Invariant with Minimization    & 23 &  0 & 54 &  0 \\
    Safety by Refinement                        & 23 &  0 & 54 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \bfc}
\label{bfc-experiments}
\end{table}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{6cm} | r | r | r | r | }
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals)      & 14 &  0 & 13 &  0 \\
    Invariant \& Invariant with Minimization    & 14 &  0 & 13 &  0 \\
    Safety by Refinement                        & 20 &  0 &  7 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \mist}
\label{mist-experiments}
\end{table}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{6cm} | r | r | r | r | }
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals)      & 2 & 0 & 36 & 0 \\
    Invariant \& Invariant with Minimization    & 2 & 0 & 26 & 0 \\
    Safety by Refinement                        & 2 & 0 & 36 & 0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \iic}
\label{iic-experiments}
\end{table}

We constructed the following two invariants by applying the method
Invariant with Minimization.

\begin{itemize}
\item \verb?firewall__no_pred_called_with_zero__depth_1__fixed?: \verb?(assert (<= l739 0))?
\item \verb?firewall__no_pred_called_with_zero__depth_2__fixed?: \verb?(assert (<= l3849 0))?
\end{itemize}
